Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-08-17 Latex/journal_v1/V5/pr.tex
add one figure

%\subsection{Summary of Simulation Results}
In figure \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
proposed algorithm (IABV) and the optimal method for URLLC service.
The minimum data rate is 5bits/sec/Hz for each UE and the maximum delay is $0.1$ms.
Also the mean arrival rate is set to be $0.2$Mbps and the mean service rate is $0.5$Mbps.
The other parameters are depicted in table \ref{table:1a}.
The optimal approach is obtained from the two-step joint exhaustive search and using CVX. 
In each iteration in the first step, the PRB allocation and O-RU association are obtained from brute force, and in the second step, we use CVX to get optimal power.
Our solution is close to the optimal value in a small number of UEs.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{optimal1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UEs }
  \label{fig:12}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.

>>>>

%\subsection{Summary of Simulation Results}
In figure \ref{fig:12}, the aggregate throughput is shown according to the number of UEs for two different methods, namely the
proposed algorithm (IABV) and the optimal method for URLLC service for the low interference.
The minimum data rate is 5bits/sec/Hz for each UE and the maximum delay is $0.1$ms.
Also the mean arrival rate is set to be $0.2$Mbps and the mean service rate is $0.5$Mbps.
The other parameters are depicted in table \ref{table:1a}.
The optimal approach is obtained from the two-step joint exhaustive search and using CVX. 
In each iteration in the first step, the PRB allocation and O-RU association are obtained from brute force, and in the second step, we use CVX to get optimal power.
Our solution is close to the optimal value in a small number of UEs.
\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{optimal1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Number of UEs }
  \label{fig:12}
\end{figure}

In figure \ref{fig:13}, the aggregate throughput is depicted vs. the maximum interference for two different maximum power thresholds of O-RU. We suppose that the maximum power threshold of UEs is one-third of the maximum power of O-RU.
%The minimum data bit rate is assumed to be 0.2Mbps for each UE.
Here we assume that with the increase of every ten dBm of interference power, it is assumed that ten users have been added to the system. In -100 dBm, we have 10 UEs, and at the end, we have 50 UEs in the system.
Since the amount of interference in the system is entered as a fixed value,
the allocation of PRBs is not considered.
The higher maximum power threshold leads to a greater aggregate throughput. 
The aggregate throughput rises with the increases of UEs and the maximum interference and then remains almost constant.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{interF.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput vs. Maximum Interference }
  \label{fig:13}
\end{figure}
\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services i.e eMBB, mMTC, and, URLLC.
The isolation of various types of services i.e eMBB, mMTC, and, URLLC in the O-DU, the O-CU, and the user plane function (UPF) is accomplished.
Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the aggregate throughput. The limited fronthaul capacity and the mean end-to-end delay for each service are considered. 
The problem is mixed-integer non-linear programming that is solved by the two-step iterative algorithm.
In the first step, we reformulated the problem to achieve the number of activated VNFs as a function of data rate. Then we obtain PRB association and power allocation using the Lagrangian method.
Then in the second step, the O-RU association is acquired.
The performance of our proposed method (IABV) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}. 
Also, we assume distinct scenarios for each service i.e eMBB, mMTC, and, URLLC based on their requirement QoS.
Simulation results depict that the proposed method (IABV) achieved $18.6\%$ higher data rate than the baseline scheme.
Moreover, simulation results illustrate more minor delays for the proposed method (IABV) than FBDR and the baseline scheme.
